% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%Section: Work Experience at the top
\sectionTitle{Professional Experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}

\begin{experiences}
  \experience
    {Present}   {Data Scientist | Digital Transformation Deparment}{Tec Milenio}{Mexico}
    {July 2021} {
                      \begin{itemize}
                        \item Ttechnical lead in the implementation of a Modern Data Stack: 
                        Fivetran (EL/Replicator) + Snowflake (DWH) + dbt (Transformation/Modeling) + Tableau (Viz)
                        \item Data Collection and Analysis, mostly in e-learning platform related topics
                        \item Data Modeling and Pipeline Design and Maintenance in Snowlflake + dbt
                        \item Support in the design of Data Products for e-learning applications
                        \item I also belong to the Data Governance Team, working with the compliance of Data Regulation and Best Practices
                      \end{itemize}
                    }
                    {Python 3, R, SQL, Snowflake, dbt, Tableau, Fivetran, PostgreSQL, Azure ML Studio, Open Web Scraper}
  \emptySeparator
  
  \experience
    {June 2021} {Data Scientist | Data Science Senior Developer}{Kalypso}{Mexico}
    {October 2020}    {
                      \begin{itemize}
                        \item Data Pipeline Engineering
                        \item Exploratory Data Analysis
                        \item Development of predictive models using ML
                        \item Linear and Non-Linear optimization of ML Models for prescriptive purposes
                      \end{itemize}
                    }
                    {Python 3, pandas, sk-learn, scipy, seaborn, PostgreSQL, Power BI}
  \emptySeparator
  
  \experience
    {October 2020}     {Data Scientist | HR Reporting \& Analytics - Strategic Workforce Planning}{Pepsico}{Mexico}
    {August 2019}    {
                      \begin{itemize}
                        \item Turnover/Churn Analysis for NFL employees
                        \item Made some python utilities to work with NLP using LDA, Sentiment Analysis and Translators with labor/environment surveys                
                        \item Data Analysis for Insight finding with Human Capital Information                   
                        \item Experiment Design and Hypotheses Testing                         
                        \item Collaboration with Global teams to implement new technologies and data science best practices                                                      
                        \item Implementation and Coordination of a HR Function in a GBS (Shared Services) framework for doing analytics with
                        Human Capital Information provided to countries in LATAM.
                        \item Key Contributor in the stabilization of SLAs (Delivery Time) from 60 to 99.9\% in 3 months.
                        \item Automation of 80\% of the operation reports with the creation and maintenance of a data pipeline made with Python and Pandas.
                        \item  Coordination of creation and maintenance of Executive Dashboards in Tableau showing Human Capital Information
                        such as People Cost, Diversity, Equity, Turnover Analysis for Talent Acquisition, etc.
                        \item Validation of Information Quality in development databases with R scripts.
                      \end{itemize}
                    }
                    {Python 3, pandas, R, tidyverse, Teradata, Tableau, Power BI, MS SharePoint, Azure Web Services}
  \emptySeparator
  
  
  \experience
    {August 2019} {Data Scientist | Digital Transformation and Innovation Department}{Axtel}{Mexico}
    {June 2018}    {
    			Design and implementation of prototypes using emergent technologies, specially automation
			and analytics in order to help and improve various tasks and assignments of the different departments in the company.
                      \begin{itemize}
                        \item Developed a Back-End project that collected information from several routers
                        of the different carriers of the company via ssh and consolidated this information in a
                        mySQL database to then expose its analytics in a website via an API made with
                        Python Flask.           
                        \item Developed a detector and classifier of manufacturing pieces with computer vision (opencv)
                        and deep learning open-source libraries (tensorflow/keras) within a co-creation framework.
                        In this project I used several CNN architectures together with other cv techinques such as
                        Template Matching, Thresholding, Morphological Operations, etc., and embedded systems, Raspberry pi and Arduino.
                        \item Mentored other department teams in their study of python and data analysis.
                      \end{itemize}
                    }
                    {Python 3, Pandas, sk-learn, scipy, seaborn, mySQL, OpenCV, Keras, RaspberryPi, Flask, SQL}
  \emptySeparator
  
  \experience
    {June 2021} {BI Analyst Jr.}{Axity}{Mexico}
    {October 2020}    {
                      \begin{itemize}
                        \item Support in Oracle and SAP tools such as Modeling in SAP Business Objects (Information Design Tool, WebIntelligence).
                        \item Data flow analysis and quality assurance between Databases (ETL) in Oracle Data Integrator.
                        \item Data Analysis and manipulation in Oracle Essbase (EAS).
                        \item Financial data analysis and validation.
                      \end{itemize}
                    }
                    {Oracle, SQL, Oracle Data Integrator, SAP Business Objects}
  \emptySeparator
  
%  \consultantexperience
%  {Février 2011}    {Ingénieur Consultant}{Altran Technologies}{France}
%  {Février 2010}    {IT Specialist}{IBM, Product Lifecycle Management Center of Excellence}
%                    {
%                      Mise en place d'un \emph{Enterprise Service Bus} (ESB) et moteur de Workflow
%                      \begin{itemize}
%                        \item Définition et implémentation de processus métiers                           
%                        \item Mise en place d'un ESB, implémentation d'un format pivot standard et définition de médiations
%                      \end{itemize}
%                    }
%                    {
%                      Websphere Integration Developer, RSA, Websphere Business Modeler, Websphere Service Registry and Repository, 
%                      Websphere Process Server, ENOVIA V6, Maximo Asset Management, Eclipse
%                    }   
%  \emptySeparator
      

\end{experiences}
